FAIR fission track analysis with geochron@home

### 2025-07-21 geochron@home/manuscript/paper.tex
Finished geochron@home supplement

\begin{abstract}
Fission track geochronology is based on the visual analysis of optical
images. This visual process is prone to observer bias. Fission track
datasets are currently reported as small data tables. The
interpretation of these tables requires a high degree of trust between
the fission track analyst and the user of the data. geochron@home is
software that removes this requirement of trust. It combines a
browser-based `virtual microscope' with an online database to provide
FAIR (Findable, Accessible, Interoperable and Reproducible) access to
fission track data.\medskip

@@

We anticipate that the introduction of FAIR workflows will make
fission track data more accurate and more future proof. Storing
fission track data online will benefit future developments in fission
track thermochronology. For example, archival datasets of peer
reviewed fission track counts can be used to train and improve machine
learning algorithms for automated fission track analysis. We hope that
other geochronological methods will follow the fission track
community's lead in FAIR data processing. This would benefit all the
other Earth Science disciplines that depend on geochronological data.
\end{abstract}

@@

\item Post-processing. The fission track data can either be downloaded
  as a flat data table of counts and area, or as a \texttt{.json} file
  containing the locations of all the counted tracks. geochron@home
  does not provide any tools to post-process these files. They are
  meant to be passed on to other tools such as spreadsheet
  applications or IsoplotR \citep{vermeesch2018c}.

@@

The five-step workflow can be used for several applications, including
(1) conventional fission track analysis; (2) archiving published
fission track results; (3) building tutorials; and (4) crowd-sourcing
fission track data. The next sections of this paper will illustrate
these four different applications with real world examples.\medskip

@@

Administrators can define regions of interest (ROI) and count or edit
the fission track coordinates of any grain in a geochron@home
database. They can also assign other users to groups, and give these
groups access to a subset of the projects in the
database. Administrators have fine control over the permissions of the
groups. For example, they can allow the members of one group to define
their own ROIs, whilst requiring members of another group to count
fission tracks in predefined ROIs.  Groups provide a mechanism to
compare and combine the results of multiple analysts of the same
sample. Figure~\ref{fig:AvP} illustrates this with two sets of fission
track density estimates (in tracks per \textmu{m}\textsuperscript{2})
for the same sample of Mount Dromedary apatite \citep{green1985b},
analysed by two users (PV and AC).\medskip

Let $N_1$ and $N_2$ be the numbers of spontaneous tracks counted by PV
and AC over areas $A_1$ and $A_2$, respectively. Then their estimated
track densities are give by $\hat{\rho}_1 = N_1/A_1$ and $\hat{\rho}_2
= N_2/A_2$. In this situation when the two areas overlap, $N_1$ and
$N_2$ cannot be treated as independent Poisson counts because the two
analysts will count some of the same tracks. It can be shown that,
under simple (ideal) assumptions, the uncertainty of the ratio of the
estimated track densities is given approximately by
\begin{equation}
  \frac{\mbox{se}(\hat{\rho}_1/\hat{\rho}_2)}{\hat{\rho}_1/\hat{\rho}_2} \approx
  \sqrt{ \frac{1}{N_1} + \frac{1}{N_2} - \frac{2\,N_0}{N_1\,N_2} }
  \label{eq:NO}
\end{equation}

@@

The radial plot of Figure~\ref{fig:AvP}b contains two sets of counts,
with $\sum N_{1} = 686$ and $\sum N_{2} = 679$, and a weighted mean
track density ratio $\hat{\rho}_{1}/\hat{\rho}_{1} = 0.94$ with
relative standard error 0.013. PV counted 600 tracks in those common
areas $A_0$, of which 549 were also counted by AC. Conversely, AC
counted 622 tracks of which 549 were also counted by PV. The ratio of
the two analysts' track density estimates based just on the common
area is therefore 600/622 = 0.965 with relative standard error 0.016,
calculated from Equation~\ref{eq:NO}. This is close to the weighted
mean ratio of 0.94 (Figure~\ref{fig:AvP}b), and is slightly nearer to
1. It indicates that PV under-counts the Mount Dromedary apatite by
3.5\% relative to AC.  The existence of `observer bias' is well
documented \citep{tamer2025}.  It is one of the reasons why fission
track analysis is often done relative to age standards: observer bias
does not have to be a problem provided that it is consistent between
grains, and between samples.\medskip

@@

The annotations in the current tutorial pages were made by an
experienced fission track analyst (Andrew Carter). This basic tutorial
provides a quick and easy mechanism to train novice users in the art
of fission track analysis. The tutorial pages are in their infancy,
and offer only a limited degree of interactivity. Users can click on
features to read the annotations. The tutorial will grow with input
from experienced analysts and future plans include the addition of
fully interactive `quizzes' (Section~\ref{sec:conclusions}). The
limitations of the current tutorials are apparent in the results of
the crowd-sourcing experiment described in the next section of this
paper.

@@

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{radialcrowd.pdf}
  \captionof{figure}{a) Box plots and summary statistics of numbers of
    spontaneous fission tracks counted in each of 25 grains by 68
    novice counters (geology students) all using the same ROIs. Each
    student counted tracks in a subset of the grains. b) The track
    counts for Grain 23 plotted against those for Grain 25 for 37
    students who counted both of those grains. c) Radial plot of the
    ratios of the counts in panel b) using the precisions given by
    Equation~\ref{eq:N12}. In each panel, the counts made by PV are
    added as blue dots.\medskip}
  \label{fig:radialcrowd}
}%\end{figure}

@@

A 1984 interlaboratory comparison study \citep{miller1985} showed that
the average of several fission track age estimates is closer to the
known age of mineral standards than the age obtained by any individual
observer. Unfortunately, routine measurement of fission track samples
by multiple analysts is prohibitively expensive in a normal laboratory
environment. geochron@home changes this, by bringing fission track
analysis to a proverbial `county fair' of citizen scientists.\medskip

Figure~\ref{fig:radialcrowd}a shows box plots and summary statistics
for the raw counts made by 68 students (two of the students were
unable to complete the assignment) for the same selection of 25 grains
that were analysed by AC and PV in Section~\ref{sec:private}. Everyone
counted tracks in the same ROIs, and counts made by PV for those ROIs
have been added as blue dots.  Variation between the mean values is to
be expected because of the differing numbers of tracks due to varying
areas and uranium contents of the grains. But the variation between
counts within grains (shown by the standard deviations) is due
entirely to differences between the students' recognising and counting
exactly the same tracks. These standard deviations increase with the
mean number of tracks and are considerable in size, being on average
about 40\% of the mean.  Also, the vast majority of students counted
fewer tracks than PV did, often many fewer. In 21 of the 25 grains,
PV's count is above the upper quartile of the students', and on 2
occasions someone counted no tracks at all.  With expert trained
counters one would expect much smaller differences between counts.
Nevertheless there are many repeated counts also.\medskip

Figure~\ref{fig:radialcrowd}b shows a scatter plot of pairs of counts
for two grains made by 33 students who counted both of them. They
average around 23 and 30 tracks per grain compared with PV's pair of
44 and 63, which is highlighted in blue. There is a positive
correlation between the pairs, consistent with systematic observer
effects (i.e., people who count a low value in one grain tend to count
similarly low in the other, and vice versa).  Comparing other pairs of
grains shows similar results, with correlations varying between 0.3
and 0.9. In all cases we have looked at, the residual variation, after
allowing for systematic differences between students, is consistent
with Poisson variation.  Figure~\ref{fig:radialcrowd}c shows a radial
plot of the ratios of the counts in Panel b, using the precisions
given by
\begin{equation}
  \frac{\mbox{se}(N_1/N_2)}{N_1/N_2}
  \approx
  \sqrt{
    \frac{1}{N_1} + \frac{1}{N_2}
  }
  \label{eq:N12}
\end{equation}

The context here is rather different from that in
Figure~\ref{fig:AvP}b, where we were comparing the ratios of counts
made by 2 analysts on each of 25 grains. Here we are comparing the
ratios of counts for the same 2 grains made by each of 33
analysts. There is no theoretical justification for
Equation~\ref{eq:N12} here, but it still provides a useful benchmark
for assessing variation between the ratios. In
Figure~\ref{fig:radialcrowd}c, that variation is consistent with
Poisson variation (as it is for most other pairs of grains) but with
expert counters one would expect less variation than that. However, in
spite of the under-counting by the students, the pooled the students'
ratio of 0.76 is quite close to PV's ratio of 0.70. This happens quite
often in this data set, but not always, and there are some pairs of
grains where the students' pooled ratio differs somewhat from
PV's.\medskip

@@

geochron@home has been in development for 10 years and
remains a work in progress. Planned improvements include:

\begin{enumerate}
\item Interactive tutorial pages. To ensure that novice users do not
  count the tails but the etch pits of fission tracks, we will add a
  `quiz' to the tutorial pages. Only users who click on the `correct'
  features in an unlabelled set of images will be allowed to count new
  samples. The pilot data of the crowd-sourcing experiment show that,
  despite the large scatter of the raw track counts obtained by the
  citizen scientists, their pairwise ratio estimates scatter evenly
  around the expert opinion. This suggests that the collective wisdom
  of the entire group of students is greater than that of the
  individual analysts. When applied to a group that has achieved a
  good level of training and experience, crowd sourcing should improve
  the precision and accuracy of fission track data.
\item Length measurements. The geochron@home archive already
  contains horizontally confined fission track measurements
  \citep{tamer2025}.  However, these results must be generated
  externally (e.g., using Fission Track Studio) and uploaded via a
  \texttt{.json} file.  The virtual microscope curently lacks the
  functionality to generate length data within
  geochron@home. This functionality will be added in a future
  update.
\item Dpar and Dper. Etch pits are currently stored as simple sets of
  x- and y-coordinates.  In reality, etch pits have a finite length
  (`Dpar') and width (`Dper'), which serve as useful indicators for
  the horizontal etch rates along the c-axis and parallel to it
  \citep{donelick1993}. Functions will be added measure and visualise
  these type of data in geochron@home.
\item Machine learning. Data science is experiencing an artificial
  intelligence revolution that has already started to transform the
  fission track method \citep{nachtergaele2020}.  Convolutional neural
  networks must be trained with example data. geochron@home
  is ideally suited for this task. Section~\ref{sec:crowdsourcing}
  showed how the collective wisdom of multiple fission track analysts
  can label fission track images with probabilities rather than
  counts. This data format is close to the form in which data are
  treated within an AI algorithm.\medskip

@@

This paper introduced geochron@home, a software platform for
FAIR fission track analysis. We demonstrated four different
applications of this platform using real data. Putting the FAIR data
paradigm into practice, all the imagery, counts and source code for
this paper are publicly available. Using these resources, the reader
can reproduce all the results that were presented in this publication.
We hope that other geochronologists will follow this example.  FAIR
data promises to address the reproducibility crisis in science
\citep{miyakawa2020}.\medskip

geochron@home's rich archive of raw data can be reanalysed in
the future. We anticipate that the adoption of FAIR data processing
workflows will open up new research opportunities. For example,
archived pairs of peer-reviewed fission track images and counts could
be used to train the next generation of automated machine learning
algorithms. Conversely, it is also possible that future improvements
in fission track images analysis will be used to update the count data
for published datasets, improved their accuracy.\medskip

@@

With the development of geochron@home, fission track geochronology is
once again ahead of the pack in terms of FAIR data analysis.
geochron@home currently only stores images and counts. This is enough
to reproduce the results of fission track studies using the external
detector method, but not for LA-ICP-MS based data. FAIR data
processing of LA-ICP-MS data requires a new generation of mass
spectrometer data reduction software. We are currently working on this
\citep{vermeesch2025b}. The development of FAIR ICP-MS data pipelines
will not only benefit fission track analysis but other chronometers as
well, such as in-situ U--Pb, Rb--Sr and Lu--Hf.\medskip

@@

\codedataavailability{geochron@home is free software released under
  the GPL-3 license. The package and its source code are available
  from \url{https://github.com/pvermees/geochron-at-home} (last
  access: April~2, 2025).  The raw data (imagery) are available at the
  geochron@home archive (\url{https://github.com/pvermees/GaHa}, last
  access: April~3, 2025).  R-scripts to reproduce the figures are
  provided in the supplementary information
  (\url{https://github.com/pvermees/supplements}, last access:
  April~3, 2025).}

@@

\authorcontribution{Pieter Vermeesch designed the study, acquired the
  funding, counted fission tracks and wrote the paper. Jiangping He
  created geochron@home. Tim Band expanded geochron@home and wrote the
  accompanying microscope image acquisition software. Andrew Carter
  provided the samples, prepared the training data and counted fission
  tracks. Rex Galbraith derived Equation~\ref{eq:NO}.}

>>>>

\begin{abstract}
Fission track thermochronology is based on the visual analysis of
optical images. This visual process is prone to observer bias. Fission
track datasets are currently reported as small data tables. The
interpretation of these tables requires a high degree of trust between
the fission track analyst and the user of the data. geochron@home is
software that removes this requirement of trust. It combines a
browser-based `virtual microscope' with an online database to provide
FAIR (Findable, Accessible, Interoperable and Reproducible) access to
fission track data.\medskip

@@

We anticipate that the introduction of FAIR workflows will make
fission track data more accurate and more future proof. Storing
fission track data online will benefit future developments in fission
track thermochronology. For example, archival datasets of peer
reviewed fission track counts can be used to train and improve machine
learning algorithms for automated fission track analysis. We invite
other geochronological methods to follow the fission track community's
lead in FAIR data processing. This would benefit all the other Earth
Science disciplines that depend on geochronological data.
\end{abstract}

@@

\item Post-processing. The fission track data can either be downloaded
  as a flat data table of counts and areas, or as a \texttt{.json}
  file containing the locations of all the counted
  tracks. geochron@home does not provide any tools to post-process
  these files. They are meant to be passed on to other tools such as
  spreadsheet applications or IsoplotR \citep{vermeesch2018c}.

@@

The five-step workflow can be used for several applications, including
(1) conventional fission track analysis; (2) archiving published
fission track results; (3) building tutorials; and (4) crowd-sourcing
fission track data. The next sections of this paper will illustrate
these applications with real world examples.\medskip

@@

Administrators can define regions of interest (ROI) and count or edit
the fission track coordinates of any grain in a geochron@home
database. They can also assign other users to groups, and give these
groups access to a subset of the projects in the
database. Administrators have fine control over the permissions of the
groups. For example, they can allow the members of one group to define
their own ROIs, whilst requiring members of another group to count
fission tracks in predefined ROIs.  Groups provide a mechanism to
compare and combine the results of multiple analysts of the same
sample. Figure~\ref{fig:AvP} illustrates this with two sets of fission
track density estimates for the same sample of Mount Dromedary apatite
\citep{green1985b}, analysed by two users (PV and AC).\medskip

Let $N_1$ and $N_2$ be the numbers of spontaneous tracks counted by
the two users over areas $A_1$ and $A_2$, respectively. Then their
estimated track densities are given by $\hat{\rho}_1 = N_1/A_1$ and
$\hat{\rho}_2 = N_2/A_2$. In this situation when the two areas
overlap, $N_1$ and $N_2$ cannot be treated as independent Poisson
counts because the two analysts will count some of the same tracks. It
can be shown that, under simple (ideal) assumptions, the uncertainty
of the ratio of the estimated track densities is given approximately
by
\begin{equation}
  \frac{\mbox{se}(\hat{\rho}_1/\hat{\rho}_2)}{\hat{\rho}_1/\hat{\rho}_2} \approx
  \sqrt{ \frac{1}{N_1} + \frac{1}{N_2} - \frac{2\,N_0}{N_1\,N_2} }
  \label{eq:NO}
\end{equation}

@@

The combined data plots of Figures~\ref{fig:AvP}b and c contain two
sets of counts, with $\sum N_{1} = 686$ and $\sum N_{2} = 679$, and a
weighted mean track density ratio $\hat{\rho}_{1}/\hat{\rho}_{1} =
0.94$ with relative standard error 0.013. PV counted 600 tracks in
those common areas $A_0$, of which 549 were also counted by
AC. Conversely, AC counted 622 tracks of which 549 were also counted
by PV. The ratio of the two analysts' track density estimates based
just on the common area is therefore 600/622 = 0.965 with relative
standard error 0.016, calculated from Equation~\ref{eq:NO}. This is
close to the weighted mean ratio of 0.94 (Figure~\ref{fig:AvP}c), and
is slightly nearer to 1. It indicates that PV under-counts the Mount
Dromedary apatite by 3.5\% relative to AC.  The existence of `observer
bias' is well documented \citep{tamer2025}.  It is one of the reasons
why fission track analysis is often done relative to age standards:
observer bias does not have to be a problem provided that it is
consistent between grains, and between samples.\medskip

@@

The annotations in the current tutorial pages were made by an
experienced fission track analyst (Andrew Carter). This basic tutorial
provides a quick and easy mechanism to train novice users in the art
of fission track analysis. The tutorial pages are in their infancy
and offer only a limited degree of interactivity. Users can click on
features to read the annotations. The tutorial will grow with input
from experienced analysts and future plans include the addition of
fully interactive `quizzes' (Section~\ref{sec:conclusions}). The
limitations of the current tutorials are apparent in the results of
the crowd-sourcing experiment described in the next section of this
paper.

@@

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{radialcrowd.pdf}
  \captionof{figure}{a) Box plots and summary statistics of numbers of
    spontaneous fission tracks counted in each of 25 grains by 68
    novice counters (geology students) all using the same ROIs. Each
    student counted tracks in a subset of the grains. b) The track
    counts for Grain 25 plotted against those for Grain 23 for 37
    students who counted both of those grains. c) Radial plot of the
    ratios of the counts in panel b) using the precisions given by
    Equation~\ref{eq:N12}. In each panel, the counts made by PV are
    added as blue dots.\medskip}
  \label{fig:radialcrowd}
}%\end{figure}

@@

An interlaboratory comparison study by \citet{miller1985} showed that
the average of several fission track age estimates is closer to the
known age of mineral standards than the age obtained by any individual
observer. Routine measurement of fission track samples by multiple
analysts is prohibitively expensive in a normal laboratory
environment. geochron@home changes this by bringing fission track
analysis to a proverbial `county fair' of citizen scientists.\medskip

Figure~\ref{fig:radialcrowd}a shows box plots and summary statistics
for the raw counts made by 68 students (two of the students were
unable to complete the assignment) for the same selection of 25 grains
that were analysed by AC and PV in Section~\ref{sec:private}. Everyone
counted tracks in the same ROIs, and counts made by PV for those ROIs
have been added as blue dots.  Variation between the mean values is to
be expected because of the differing numbers of tracks due to varying
areas and U contents of the grains. But the variation between counts
within grains (shown by the standard deviations) is due entirely to
differences between the students' recognising and counting exactly the
same tracks. These standard deviations increase with the mean number
of tracks and are considerable in size, being on average about 40\% of
the mean.  Also, the vast majority of students counted fewer tracks
than PV did, often many fewer. In 21 of the 25 grains, PV's count is
above the upper quartile of the students', and on two occasions
someone counted no tracks at all.  With expert trained counters one
would expect much smaller differences between counts.  Nevertheless
there are many repeated counts also.\medskip

Figure~\ref{fig:radialcrowd}b shows a scatter plot of pairs of counts
for two grains made by 37 students who counted both of them. They
average around 29 and 30 tracks per grain compared with PV's pair of
52 and 50, which is highlighted in blue. There is a positive
correlation between the pairs, consistent with systematic observer
effects (i.e., people who count a low value in one grain tend to count
similarly low in the other, and vice versa).  Comparing other pairs of
grains shows similar results, with correlations varying between 0.3
and 0.9. In all cases we have looked at, the residual variation, after
allowing for systematic differences between students, is consistent
with Poisson variation.  Figure~\ref{fig:radialcrowd}c shows a radial
plot of the ratios of the counts in Panel~b, using the precisions
given by
\begin{equation}
  \frac{\mbox{se}(N_1/N_2)}{N_1/N_2}
  \approx
  \sqrt{
    \frac{1}{N_1} + \frac{1}{N_2}
  }
  \label{eq:N12}
\end{equation}

The context here is rather different from that in
Figure~\ref{fig:AvP}b, where we were comparing the ratios of counts
made by two analysts on each of 25 grains. Here we are comparing the
ratios of counts for the same two grains made by each of 37
analysts. There is no theoretical justification for
Equation~\ref{eq:N12} here, but it still provides a useful benchmark
for assessing variation between the ratios. In
Figure~\ref{fig:radialcrowd}c, that variation is consistent with
Poisson variation (as it is for most other pairs of grains) but with
expert counters one would expect less variation than that. However, in
spite of the under-counting by the students, the pooled students'
ratio of 0.76 is close to PV's ratio of 0.70. This happens quite
often in this data set, but not always, and there are some pairs of
grains where the students' pooled ratio differs somewhat from
PV's.\medskip

@@

geochron@home has been in development for a decade and remains a work
in progress. Planned improvements include:

\begin{enumerate}
\item Interactive tutorial pages. To ensure that novice users do not
  count the tails but the etch pits of fission tracks, we will add a
  `quiz' to the tutorial pages. Only users who click on the `correct'
  features in an unlabelled set of images will be allowed to count new
  samples. Section~\ref{sec:crowdsourcing} shows that, despite the
  large scatter of the raw track counts obtained by the citizen
  scientists, their pairwise ratio estimates scatter evenly around the
  expert opinion. This suggests that the collective wisdom of the
  entire group of students is greater than that of the individual
  analysts. When applied to a group that has achieved a good level of
  training and experience, crowd sourcing should improve the precision
  and accuracy of fission track data.
\item Length measurements. The geochron@home archive already
  contains horizontally confined fission track measurements
  \citep{tamer2025}.  However, these results must be generated
  externally (e.g., using Fission Track Studio) and uploaded via a
  \texttt{.json} file.  The virtual microscope curently lacks the
  functionality to generate length data within
  geochron@home. This functionality will be added in a future
  update.
\item Dpar and Dper. Etch pits are currently stored as simple sets of
  x- and y-coordinates.  In reality, etch pits have a finite length
  (`Dpar') and width (`Dper'), which serve as useful indicators for
  the horizontal etch rates along the c-axis and parallel to it
  \citep{donelick1993}. Functions will be added to measure and
  visualise this type of data in geochron@home.
\item Machine learning. Data science is experiencing an artificial
  intelligence revolution that has already started to transform the
  fission track method \citep{nachtergaele2020}.  Convolutional neural
  networks must be trained with example data. geochron@home
  is ideally suited for this task. Section~\ref{sec:crowdsourcing}
  showed how the collective wisdom of multiple fission track analysts
  can label fission track images with probabilities rather than
  counts. This data format is close to the form in which data are
  treated within an AI algorithm.\medskip

@@

This paper introduced geochron@home, a software platform for FAIR
fission track analysis. We demonstrated four different applications of
this platform using real data. Putting the FAIR data paradigm into
practice, all the imagery, counts and source code for this paper are
publicly available. Using these resources, the reader can reproduce
all the results that were presented in this publication.  We encourage
other geochronologists to follow this example.  FAIR data promises to
address the reproducibility crisis in science
\citep{miyakawa2020}.\medskip

geochron@home's rich archive of raw data can be reanalysed in
the future. We anticipate that the adoption of FAIR data processing
workflows will open up new research opportunities. For example,
archived pairs of peer-reviewed fission track images and counts could
be used to train the next generation of automated machine learning
algorithms. Conversely, it is also possible that future improvements
in fission track images analysis will be used to update the count data
for published datasets, improving their accuracy.\medskip

@@

With the development of geochron@home, fission track thermochronology
is once again ahead of the pack in terms of FAIR data analysis.
geochron@home currently only stores images and counts. This is enough
to reproduce the results of fission track studies using the external
detector method, but not for LA-ICP-MS based data. FAIR data
processing of LA-ICP-MS data requires a new generation of mass
spectrometer data reduction software. We are currently working on this
\citep{vermeesch2025b}. The development of FAIR ICP-MS data pipelines
will not only benefit fission track analysis but other chronometers as
well, such as in-situ U--Pb, Rb--Sr and Lu--Hf.\medskip

@@

\codedataavailability{geochron@home is free software released under
  the GPL-3 license. The package and its source code are available
  from \url{https://github.com/pvermees/geochron-at-home} (last
  access: July~21, 2025).  The raw data (imagery) are available at the
  geochron@home archive (\url{https://github.com/pvermees/GaHa}, last
  access: July~21, 2025).  R-scripts to reproduce the figures are
  provided in the supplementary information
  (\url{https://github.com/pvermees/supplements}, last access:
  July~21, 2025).}

@@

\authorcontribution{Pieter Vermeesch designed the study, acquired the
  funding, counted fission tracks and wrote the paper. Jiangping He
  created geochron@home. Tim Band expanded geochron@home and wrote the
  accompanying microscope image acquisition software. Andrew Carter
  provided the samples, prepared the training data and counted fission
  tracks. Rex Galbraith derived Equation~\ref{eq:NO} and verified all
  the other calculations.}
